---
title: "homework3"
author: "Ben Tanaka"
date: "5/20/2019"
output: 
  html_document:
    keep_md: true
---

# *Homework Question 1*
### Question 1:  Git commands
* mkdir homework3
* cd /users/ben/documents/r/homework3
* git clone https://github.com/caesar0301/awesome-public-datasets


### Question 2a:
```{r}
df <- read.csv(file="/users/ben/documents/r/homework3/awesome-public-datasets/datasets/titanic.csv",header=TRUE,sep=",")

```

### Question 2b:
```{r}
library(plyr)
sex<-count(df,'Sex')
library(ggplot2)
sexplot<-ggplot(sex,aes(Sex,freq))+geom_bar(stat="identity")+ggtitle("Total Passengers by Sex")+xlab("Gender")+ylab("Total Counts")

sexplot

```

### Question 2c:
```{r}
q2c <- list(age=df$Age, fare=df$Fare, survived=df$Survived)
q2c_means <- lapply(q2c,mean,na.rm=TRUE)
as.data.frame(q2c_means)

```

### Question 3a-d:
```{r}
sleep <- read.csv(file="http://talklab.psy.gla.ac.uk/L1_labs/lab_1/homework/sleep_data_01.csv", header=TRUE,sep=",")

sleep_data <- function (tablename)
{

median_age <- median(tablename$Age,na.rm=TRUE)
min_dur <- min(tablename$Duration,na.rm=TRUE)
max_dur <- max(tablename$Duration,na.rm=TRUE)
mean_RSES <- mean(tablename$RSES,na.rm=TRUE)
sd_RSES <- sd(tablename$RSES,na.rm=TRUE)


list_vars <- list(median_age=median_age,mean_RSES=mean_RSES,sd_RSES=sd_RSES/5,Range_Duration=max_dur-min_dur)

report<-as.data.frame(list_vars)

library(data.table)
setnames(report,old=c("median_age","mean_RSES","sd_RSES","Range_Duration"),new=c("MedianAge","SelfEsteem","SE_SD","DurationRange"))

round(report,2)

}
```

# Question 3e:
```{r}
sleep_data(sleep)
```

# Question 4a:
```{r}
library(fivethirtyeight)
```

# Question 4b:
```{r}
library(fivethirtyeight)
df<-data.frame(college_recent_grads)
head(df)

```

# Question 4c:


This is a link to the recent college grads article [Recent College Grads](http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/)



# Question 4d:
```{r}
dim(df)
colnames(df)

```


# Question 5a:
```{r}
colnames(df)
ncol(df)

```

# Question 5b:
```{r}
library(dplyr)

major_count <- df %>% group_by(major_category) %>% summarise(n_distinct(major))

setnames(major_count,old=c("n_distinct(major)"),new=c("Total_Counts"))

```

# Question 5c:
```{r Major_Category, echo=FALSE}
library(ggplot2)

ggplot(major_count,aes(x=major_category, y=Total_Counts, color=major_category)) + geom_bar (stat="identity") + theme(axis.text.x=element_text(angle=90,hjust=1)) + coord_flip()

par(las=2)
barplot(major_count$Total_Counts, main="Total Counts by Major Cateogry",names.arg=major_count$major_category, horiz=TRUE,xlab="Major Category", ylab="Total Counts", col = "darkblue")

```

# Question 5d:
```{r}
write.csv(df, file = "mydf.csv",row.names=FALSE)
```

# Link to GITHUB
This is the link to the GITHUB repository:  [Homework3_Repository](https://github.com/bendexter/SMU-MSDS-Homework/tree/Homework3)
